% !TeX root = /../Report.tex

\chapter*{Abstract\markboth{Abstract}{Abstract}}
\addcontentsline{toc}{chapter}{\protect\numberline{}Abstract}
\label{abstract}

Writing a good scientific thesis or publication is challenging.
To provide you a little support when starting to write your thesis, this template contains some hints and general advices.

In chapter~\ref{sec:working} you will find hints and examples on how to work with \LaTeX .
This section origins from the IMRT\footnote{Institute for Dynamic Systems and Control, ETH Zurich; www.imrt.ethz.ch} \LaTeX ~template by Eric Mueller (2009) and Soren Ebbesen (2013).

However, there are also general hints that apply for all sections and paragraphs of scientific writing. These general hints are placed at the beginning of chapter~\ref{scientificWriting}.
These general hints are mainly based on~\cite{zeiger2000ewb}, sometimes the sentences are reformulated or selected, but there are also sections that are copied 1-to-1 from the book.

The sections about the different components of a scientific work in chapter~\ref{scientificWriting} are mainly taken from a writing tutorial by Olivier, M-C and James from the ReLab\footnote{Rehabilitation Engineering Lab, ETH Zurich; www.relab.ethz.ch}, with neither asking them for their consent nor citing them correctly. There are also copied passages from their tutorial without citing their original sources.

\textbf{This is plagiarism, you are not allowed to do so in your thesis and are recommended to read section~\ref{AboutPlagiarism} about plagiarism!!!}

This file is for internal use at the SMS lab only. Based on the fact that citation rules are not respected, do not share or publish this template as is.

\vspace{1.0cm}

Please feel free to contact me for feedbacks or ideas how to improve this template: 

gerig.nicolas@hest.ethz.ch

\chapter*{\"Uberblick\markboth{\"Uberblick}{\"Uberblick}}
\addcontentsline{toc}{chapter}{\protect\numberline{}\"Uberblick}
\label{ueberblick}

	This is where you put a German translation of your abstract.
	Please ask your supervisor if this is required.
